---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

```{r, message=FALSE, warning=FALSE, r,echo=FALSE}
library(knitr)
```

# BUSULFAN APP

This repository contains two folders:  

* *sim*: materials to run a simulation study to quantify the interest of therapeutic drug monitoring to manage the inter-individual variability of exposure to busulfan.  
* *app*: a shiny application for model-informed precision dosing of busulfan in Thai pediatric patients.  

Both rely on [mapbayr](https://github.com/FelicienLL/mapbayr), a package dedicated to MAP-Bayesian estimation of PK parameters in R.

# Disclaimer

The application was developped as a proof-of-concept of a model-informed precision dosing software dedicated to the calculation of doses of busulfan in the Thai pediatric population. It is meant to be used for research, educational and communication purposes. It comes with no guarantee. It is not an electronic medical device. The authors of this application are not responsible for the use of this application in a clinical context for the treatment of actual patients.

# Installation
Clone the repository or download its content in a .zip file after clicking on the green "Code" icon.

Note that the following packages, and their dependencies, are required to make the application work: 

```{r, eval = FALSE}
install.packages("mapbayr") # and mrgsolve dependency
install.packages("shiny")
install.packages("tidyr") # and tibble and dplyr dependencies
install.packages("lubridate")
install.packages("rhandsontable")
```

If you are using a Windows computer, you need to have Rtools installed to compile C++. Visit [the CRAN website](https://cran.r-project.org/bin/windows/Rtools/) for more information.

While it is installed, launch the application in the script called "app/app.R"